---
title: "On the development of this app"
date: "`r Sys.Date()`"
author: "Daniel Amieva Rodriguez"
output:
  rmdformats::downcute:
    downcute_theme: chaos
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)

pacman::p_load(googlesheets4,
               dplyr,
               rmdformats,
               here,
               gt,
               gtExtras,
               DT,
               janitor)

here::i_am("developing_the_static_site.Rmd")

source(
  here::here("R","fetch_poly_directory.R")
)

directorio_df <- fetch_poly_directory() %>% 
  janitor::clean_names()

tally_this <- function(data,
                       column){
  
 basic_kable <- data %>% 
   group_by({{column}}) %>% 
  count() %>% 
  rename("# de terapeutas" = n) %>% 
  arrange(desc(`# de terapeutas`)) %>% 
  knitr::kable(.)
 
 return(basic_kable)
}

```

## Objetive

This space is used for developing visualization ideas.

Considering that the dataset has many potential filter columns its important to think of ways to be able to select any of these in a few clicks. UX is the most important focus of this project given that the data is already [freely provided for](https://docs.google.com/spreadsheets/d/1Kc_kCvysiwwWssyRsgtmAvx2HeB0WcAW0MagakIwORY/htmlview) and looking through a spreadsheet of `r ncol(directorio_df)` columns and `r nrow(directorio_df)` records can be overwhelming to decide which type of filter to implement. 

My current idea is to tally the category to measure the most repeated values to see if *that can guide what kind of slicer to implement.

Inicial la pagina web estatica puede dar la opcion de escoger entre:
 - escoger por presencial o en linea: **modalidad** y **ciudad** requires parsing into 2 and categorized. I dont want to do parsing so maybe I can tokenize **institucion, especialidad, 


## Raw Data

For now Dt table holds the most promise for simple searbox interface

```{r rawtable}
DT::datatable(directorio_df)
```


## Tally Titulo

This gives a good view of a basic question. Can sexologos not be psicologos? We dont reclassify cause the current categories have a encoded gender information which is relevant.

[Center values. maybe allow to drilldown]

```{r tallytitulo}
directorio_df %>% 
  tally_this(titulo) 
```

## Tally Enfoque de terapia

```{r tallyenforque}
directorio_df %>% 
  tally_this(enfoque_de_la_terapia) 
  
```

## Tally Modalidad

```{r tallymodalidad}
directorio_df %>%
  tally_this(modalidad) 
  
```

## Tally Especialidad

```{r tallyespecialidad}
directorio_df %>% 
  tally_this(especialidad) 
```

## Tally Ciudad

```{r tallyciudad}
directorio_df %>% 
  tally_this(ciudad_y_zona_donde_se_encuentra_su_consultorio)  
```
